### 2017-05-13 manuscript/usses_water_ms.Rmd
trivial update to figure 1

TABLES
------

@@

>>>>

Tables
------

@@

Figures
-------

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{../figures/histppt_and_anpptrend.png}
  \caption{(A) Histogram of historical precipitation from 1926-2016, with the years of the experiment overlaid as colored points. ``Drought'' treatments (squares) are shown as a 50\% reduction from the observed precipitation. ``Irrigation'' treatment precipitation levels are not shown. (B) Mean (points) ANPP and its standard deviation (error bars) for each year of the experiment.}
\end{figure}
